%-------------------------
% Resume - Ishan Singh
%-------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage[margin=0.5in, top=0.4in, bottom=0.4in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{charter}
\usepackage[hidelinks,
  pdftitle={Ishan Singh - Resume},
  pdfauthor={Ishan Singh},
  pdfsubject={Backend / Platform Engineer},
  pdfkeywords={Go, Python, Kubernetes, AWS, Kafka, IAM, distributed systems, microservices}
]{hyperref}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{microtype}

\linespread{1.08}\selectfont
\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}
\urlstyle{same}

% Better line wrapping
\raggedright
\setlength{\emergencystretch}{3em}
\hyphenpenalty=10000
\exhyphenpenalty=10000

% Section styling
\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\vspace{-3pt}\titlerule]

\titlespacing*{\section}{0pt}{9pt}{5pt}

% Lists
\newenvironment{resumeList}{
  \begin{itemize}[
    leftmargin=0.22in,
    label=\textbullet,
    itemsep=2pt,
    topsep=2.5pt,
    parsep=0pt,
    partopsep=0pt
  ]
}{
  \end{itemize}
  \vspace{0pt}
}

% Experience heading
\newcommand{\resumeSubheading}[4]{
  \vspace{3pt}
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{#3} & \textit{#4} \\
  \end{tabular*}
  \vspace{-5pt}
}

%-------------------------------------------
\begin{document}

%----------HEADING-----------------
\begin{center}
  {\LARGE \textbf{Ishan Singh}} \\[1pt]
  \href{mailto:ishan.singh024@gmail.com}{ishan.singh024@gmail.com}
  \textbar{} +91-9457710212
  \textbar{} \href{https://linkedin.com/in/proishan11}{linkedin.com/in/proishan11}
  \textbar{} \href{https://proishan11.github.io}{proishan11.github.io}
\end{center}

\vspace{-8pt}

%-----------SUMMARY-----------------
\section{Summary}
Backend / Platform Engineer with 6+ years of experience building distributed systems, multi-tenant SaaS platforms, IAM, real-time data pipelines, and Kubernetes-native backend services at scale.

%-----------SKILLS-----------------
\section{Technical Skills}
\textbf{Languages:} Go, Python, Java, C/C++, SQL \\
\textbf{Backend / Infra:} Kubernetes, AWS, Kafka, PostgreSQL, ClickHouse, REST, GraphQL \\
\textbf{Security / Observability:} IAM, SSO (SAML, OIDC), Splunk, CloudWatch \\
\textbf{AI / Infra:} AWS Bedrock, MCP, LLMs, LangChain, RAG, Qdrant, pgvector

%-----------EXPERIENCE-----------------
\section{Experience}

\resumeSubheading
  {Cisco}{Bengaluru, KA}
  {Software Engineer}{Oct. 2024 -- Present}
\begin{resumeList}
  \item Built tenant-scale global search for Cisco Secure Access using Go, OpenSearch, DynamoDB, and Kafka, indexing 30+ security configuration object types across 50+ searchable fields and millions of cross-object relationships.
  \item Enabled nested and where-used lookups to trace related objects, policies, and dependencies -- targeting 60\% lower policy-troubleshooting MTTR and 40\% fewer audit misconfigurations.
  \item Designed anomaly schemas, RCA service APIs (Go), and deployment pipelines (Terraform, Kubernetes) for an internal root-cause analysis platform; shipped MCP servers in Python with Bedrock-powered agents.
  \item Led implementation of a distributed firewall log ingestion and enrichment pipeline processing 10K events/sec using Go, Kafka, Kinesis, DynamoDB, and S3 with no upstream lag.
\end{resumeList}

\resumeSubheading
  {Deepfactor, acquired by Cisco}{Bengaluru, KA}
  {Senior Software Engineer}{Feb. 2023 -- Oct. 2024}
\begin{resumeList}
  \item Designed and built the IAM layer using Keycloak and Postgres for Deepfactor SaaS beta, supporting multi-tenant authentication and authorization across SaaS and on-prem deployments.
  \item Implemented generic enterprise SSO support using SAML and OIDC, enabling customer-managed identity provider integrations.
  \item Designed per-tenant rate limiting at the Kubernetes ingress layer using Istio and custom usage metrics from ClickHouse such as telemetry data ingested and containers observed.
  \item Built team management and role-scoped access controls for secure multi-tenant collaboration.
\end{resumeList}

\resumeSubheading
  {Amazon}{Bengaluru, KA}
  {Software Development Engineer}{Jul. 2021 -- Jan. 2023}
\begin{resumeList}
  \item Led organization-wide platform migration automation in Java for 50+ teams, reducing a multi-day manual process to a minutes-long workflow.
  \item Contributed to AIWorkbench (Java), a no-code workflow platform for composing chained workflows across AWS and internal services.
  \item Built approval workflows that paused execution to validate intermediate ML inference results before continuing downstream processing.
  \item Built a one-click campaign launcher in Python using ML inference outputs to recommend campaign configurations during large-scale marketplace events.
\end{resumeList}

\resumeSubheading
  {Optum, UnitedHealth Group}{Remote}
  {Software Engineer}{Aug. 2020 -- Jun. 2021}
\begin{resumeList}
  \item Built a service in Java to validate Kafka streams against source databases and generate automated data quality reports.
  \item Migrated legacy services from Java to Go and added observability using Prometheus, Grafana, and Jaeger.
\end{resumeList}

\resumeSubheading
  {Mindship}{Bengaluru, KA}
  {Software Engineer Intern}{Jun. 2019 -- Sep. 2019}
\begin{resumeList}
  \item Built reusable backend services in Go including a GraphQL-based web chat service and messaging integrations with Twilio and SendGrid.
\end{resumeList}

\newpage

%-----------PROJECTS-----------------
\section{Projects}
\textbf{\href{https://github.com/proishan11/open-agent-policy}{Open Agent Policy}}: Zero-trust access control framework for AI agents with a Python SDK and a policy engine written in Go. \\[2pt]
\textbf{\href{https://github.com/proishan11/gowal}{Distributed WAL}}: Disk-backed distributed write-ahead log in Go with Raft-based replication, leader election, and fault-tolerant recovery. \\[2pt]
\textbf{Lox Interpreter}: Tree-walking interpreter for the Lox language in Go, featuring lexical analysis, recursive-descent parsing, and AST evaluation. \\[2pt]
\textbf{\href{https://github.com/proishan11/VirtualStylus}{Virtual Stylus}}: Hand-gesture-driven drawing interface built in Python with real-time object detection and classification for touchless HCI.

%-----------EDUCATION-----------------
\section{Education}
\resumeSubheading
  {Zakir Husain College of Engineering \& Technology, AMU}{Aligarh, UP}
  {Bachelor of Computer Engineering; GPA: 9.12/10}{Aug. 2016 -- May 2020}

%-------------------------------------------
\end{document}
